Synpotic Soil Characterization

### 2025-02-18 3-reports/manuscript_figures.Rmd
figures for poster

@@

@@

```{r v2-scaled_gg2_split-NEW, fig.height = 10, fig.width = 14}
library(ggh4x) # for nested facets
# https://teunbrand.github.io/ggh4x/reference/facet_nested.html

>>>>

```{r map-poster, fig.height = 9.5, fig.width = 13}

## Make the base map
base_plot <- 
  ggplot() + 
  geom_sf(data = region) + 
  #   geom_sf_text(data = st_labels, aes(label = STUSPS))+
  geom_point(
    data = sites, aes(x, y),
    size = 2, color = "black")+
  # CB inset rectangle
  geom_rect(aes(xmin = -77.8, xmax = -74.5, ymin = 36.8, ymax = 40.5), 
            fill = NA, color = "black", lwd = 0.75) +
  geom_segment(aes(x = -74.5, xend = -70, y = 38, yend = 38), 
               color = "black", lwd = 0.75) + 
  # WLE inset rectangle
  geom_rect(aes(xmin = -84, xmax = -82, ymin = 41, ymax = 42), 
            fill = NA, color = "black", lwd = 0.75) +
  geom_segment(aes(x = -83, xend = -83, y = 42, yend = 44), 
               color = "black", lwd = 0.75) + 
  annotation_north_arrow(location = "tr", which_north = "true", 
                         pad_x = unit(0.0, "in"), pad_y = unit(0.2, "in"),
                         style = north_arrow_fancy_orienteering)+
  xlim(-92, -67)+
  ylim(35, 49)+
#  scale_x_continuous(labels = NULL)+
#  scale_y_continuous(labels = NULL)+
  theme(legend.background = element_rect(fill = alpha("white", 0.0)), 
        legend.key = element_rect(fill = "transparent"), 
        legend.position = c(0.85, 0.1),
        axis.text = element_blank()) + 
  labs(x = "", y = "")+
  theme_void()+
  NULL

## Combine into single figure
base_plot + 
  annotation_custom(
    ggplotGrob(inset_plot_wle), 
    xmin = -90, xmax = -80, ymin = 42, ymax = 50)+
  annotation_custom(
    ggplotGrob(inset_plot_cb), 
    xmin = -75, xmax = -65, ymin = 35, ymax = 43)

@@

```{r v2-pca_gg_regions-poster, fig.width=7, fig.height=7}

gg_pca_wle = 
  ggbiplot(pca_overall_wle$pca_int, obs.scale = 1, var.scale = 1, varname.size = 5,
           groups = as.character(pca_overall_wle$grp$transect), 
           ellipse = TRUE, circle = FALSE, var.axes = TRUE, alpha = 1) +
  geom_point(size=5,stroke=1, alpha = 1,
             aes(shape = pca_overall_wle$grp$site,
                 fill = groups), 
             stroke = 1)+ 
  scale_color_manual(breaks = c("upland", "transition", "wte", "wetland"), 
                     values = pal_transect)+
  scale_fill_manual(breaks = c("upland", "transition", "wte", "wetland"), 
                    values = pal_transect)+
  scale_shape_manual(values = c(21, 24, 22))+
  xlim(-3, 5)+
  ylim(-2.5, 3.5)+
  labs(shape="", fill = "", color = "", title = "Lake Erie")+ 
  theme_kp()+
  theme(legend.position = "top", legend.box = "vertical",
        plot.title = element_text(face = "bold", size = 18))+
  guides(fill = guide_legend(override.aes = list(alpha=1, shape = 21, size = 3)))+
  NULL

gg_pca_cb = 
  ggbiplot(pca_overall_cb$pca_int, obs.scale = 1, var.scale = 1, varname.size = 5,
           groups = as.character(pca_overall_cb$grp$transect), 
           ellipse = TRUE, circle = FALSE, var.axes = TRUE, alpha = 0) +
  geom_point(size=5,stroke=1, alpha = 1,
             aes(shape = pca_overall_cb$grp$site,
                 fill = groups), 
             stroke = 1)+ 
  scale_color_manual(breaks = c("upland", "transition", "wte", "wetland"), 
                     values = pal_transect)+
  scale_fill_manual(breaks = c("upland", "transition", "wte", "wetland"), 
                    values = pal_transect)+
  scale_shape_manual(values = c(21, 24, 22))+
  xlim(-5, 3)+
  ylim(-2.5, 3.5)+
  labs(shape="", fill = "", color = "", title = "Chesapeake Bay")+ 
  theme_kp()+
  theme(legend.position = "top", legend.box = "vertical",
        plot.title = element_text(face = "bold", size = 18))+
  guides(fill = guide_legend(override.aes = list(alpha=1, shape = 21, size = 3)))+
  NULL

gg_pca_regions = cowplot::plot_grid(gg_pca_wle , gg_pca_cb, nrow = 2,
                                    labels = c("Lake Erie", "Chesapeake Bay"))
#gg_pca_regions

gg_pca_wle
gg_pca_cb

@@

```{r v2-scaled_gg2_split-NEW, fig.height = 10, fig.width = 12}
library(ggh4x) # for nested facets
# https://teunbrand.github.io/ggh4x/reference/facet_nested.html
